### 2017-03-03 robust-software.tex
Fixups from PR; added Software Carpentry URL to affiliation

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section*{#1}}
\newcommand{\ruleminor}[1]{\textbf{#1}}
\begin{document}
\vspace*{0.2in}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Making Research Software More Robust}
}
\newline
\\
{Morgan~Taschuk}\textsuperscript{1,\ddag *},
{Greg~Wilson}\textsuperscript{2,\ddag}
\\
\textbf{1} Ontario Institute for Cancer Research / morgan.taschuk@oicr.on.ca
\\
\textbf{2} Software Carpentry Foundation / gvwilson@software-carpentry.org
\\
\bigskip
{\ddag} These authors contributed equally to this work.
\\
* Corresponding author.
\end{flushleft}

@@

\emph{S1 Checklist. Robust software checklist.} A checklist summarizing these ten simple rules to apply to your own
software.

\begin{thebibliography}{10}

\bibitem{prins2015}
Prins P, de~Ligt J, Tarasov A, Jansen RC, Cuppen E, Bourne PE.
\newblock Toward effective software solutions for big biology.
\newblock Nature Biotechnology. 2015;33(7):686--687.
\newblock doi:{10.1038/nbt.3240}.

\bibitem{baker2016}
Baker M.
\newblock 1,500 scientists lift the lid on reproducibility.
\newblock Nature. 2016;533(7604):452--454.
\newblock doi:{10.1038/533452a}.

\bibitem{prabhu2011}
Prabhu P, Jablin TB, Raman A, Zhang Y, Huang J, Kim H, et~al.
\newblock A Survey of the Practice of Computational Science.
\newblock In: State of the Practice Reports. SC '11. New York, NY, USA: ACM;
  2011. p. 19:1--19:12.

\bibitem{lawlor2015}
Lawlor B, Walsh P.
\newblock Engineering bioinformatics: building reliability, performance and
  productivity into bioinformatics software.
\newblock Bioengineered. 2015;6(4).
\newblock doi:{10.1080/21655979.2015.1050162}.

\bibitem{ison2016}
Ison J, Rapacki K, Ménager H, Kalaš M, Rydza E, Chmura P, et~al.
\newblock Tools and data services registry: a community effort to document
  bioinformatics resources.
\newblock Nucleic Acids Research. 2016;44(D1):D38--D47.
\newblock doi:{10.1093/nar/gkv1116}.

\bibitem{brazas2012}
Brazas MD, Yim D, Yeung W, Ouellette BFF.
\newblock A decade of web server updates at the bioinformatics links directory:
  2003-–2012.
\newblock Nucleic Acids Research. 2012;doi:{10.1093/nar/gks632}.

\bibitem{stajich2002}
Stajich JE, Block D, Boulez K, Brenner SE, Chervitz SA, Dagdigian C, et~al.
\newblock The Bioperl Toolkit: Perl Modules for the Life Sciences.
\newblock Genome Research. 2002;12(10):1611--1618.
\newblock doi:{10.1101/gr.361602}.

\bibitem{Seemann2013}
Seemann T.
\newblock Ten recommendations for creating usable bioinformatics command line
  software.
\newblock GigaScience. 2013;2(1):15.
\newblock doi:{10.1186/2047-217X-2-15}.

\bibitem{nekrutenko2012}
Nekrutenko A, Taylor J.
\newblock Next-generation sequencing data interpretation: enhancing
  reproducibility and accessibility.
\newblock Nature ReviewsGenetics. 2012;13(9):667--72.
\newblock doi:{10.1038/nrg3305}.

\bibitem{atwood2015}
Atwood TK, Bongcam-Rudloff E, Brazas ME, Corpas M, Gaudet P, Lewitter F, et~al.
\newblock GOBLET: The Global Organisation for Bioinformatics Learning,
  Education and Training.
\newblock PLoS Computational Biology. 2015;doi:{10.1371/journal.pcbi.1004143}.

\bibitem{sanders2008}
Sanders R, Kelly D.
\newblock Dealing with Risk in Scientific Software Development.
\newblock Software, IEEE. 2008;25(4):21--28.
\newblock doi:{10.1109/ms.2008.84}.

\bibitem{afgan2016}
Afgan E, Baker D, van~den Beek M, Blankenberg D, Bouvier D, Čech M, et~al.
\newblock The Galaxy platform for accessible, reproducible and collaborative
  biomedical analyses: 2016 update.
\newblock Nucleic Acids Research. 2016;44(W1):W3--W10.
\newblock doi:{10.1093/nar/gkw343}.

\bibitem{howe2012}
Howe B.
\newblock Virtual Appliances, Cloud Computing, and Reproducible Research.
\newblock Computing in Science Engineering. 2012;14(4):36--41.
\newblock doi:{10.1109/MCSE.2012.62}.

\bibitem{gentleman2004}
Gentleman RC, Carey VJ, Bates DM, Bolstad B, Dettling M, Dudoit S, et~al.
\newblock Bioconductor: open software development for computational biology and
  bioinformatics.
\newblock Genome Biology. 2004;5(10):1--16.
\newblock doi:{10.1186/gb-2004-5-10-r80}.

\bibitem{varoquaux2015}
Varoquaux G. Software for reproducible science: let’s not have a
  misunderstanding; 2015.
\newblock
  \url{http://gael-varoquaux.info/programming/software-for-reproducible-science-lets-not-have-a-misunderstanding.html}.

\bibitem{brown2013}
Brown CT. Replication, reproduction, and remixing in research software; 2013.
\newblock \url{http://ivory.idyll.org/blog/research-software-reuse.html}.

\bibitem{wilson2014}
Wilson G, Aruliah DA, Brown CT, Hong NPC, Davis M, Guy RT, et~al.
\newblock Best Practices for Scientific Computing.
\newblock PLoS Biology. 2014;12(1):e1001745.
\newblock doi:{10.1371/journal.pbio.1001745}.

\bibitem{wilson2016}
Wilson G, Bryan J, Cranston K, Kitzes J, Nederbragt L, Teal TK.
\newblock Good Enough Practices in Scientific Computing.
\newblock arxivorg. 2016;abs/1609.00037.

\bibitem{noble2009}
Noble WS.
\newblock {A Quick Guide to Organizing Computational Biology Projects}.
\newblock PLoS Computational Biology. 2009;5(7).
\newblock doi:{10.1371/journal.pcbi.1000424}.

\bibitem{blischak2016}
Blischak JD, Davenport ER, Wilson G.
\newblock A Quick Introduction to Version Control with Git and GitHub.
\newblock PLOS Computational Biology. 2016;12(1):1--18.
\newblock doi:{10.1371/journal.pcbi.1004668}.

\bibitem{karimzadeh2016}
Karimzadeh M, Hoffman MM. Creating great documentation for bioinformatics
  software; 2016.
\newblock \url{http://hdl.handle.net/1807/73111}.

\bibitem{Johnson1997}
Johnson M.
\newblock Building a Better ReadMe.
\newblock Technical Communication. 1997;44(1):28--36.

\bibitem{gnustandards}
{\relax Free Software Foundation}. GNU Coding Standards; 2016.
\newblock \url{https://www.gnu.org/prep/standards/standards.html}.

\bibitem{posix2016}
{\relax The IEEE}, {\relax The Open Group}. The Open Group Base Specifications
  Issue 7 IEEE Std 1003.1-2008. 12. Utility Conventions; 2016.
\newblock
  \url{http://pubs.opengroup.org/onlinepubs/9699919799/basedefs/V1_chap12.html}.

\bibitem{pertea2016}
Pertea M, Kim D, Pertea GM, Leek JT, Salzberg SL.
\newblock Transcript-level expression analysis of RNA-seq experiments with
  HISAT, StringTie and Ballgown.
\newblock Nature Protocols. 2016;11(9):1650--1667.

\bibitem{steinmacher2015}
Steinmacher I, Silva MAG, Gerosa MA, Redmiles DF.
\newblock A systematic literature review on the barriers faced by newcomers to
  open source software projects.
\newblock Information and Software Technology. 2015;59:67 -- 85.
\newblock doi:{http://dx.doi.org/10.1016/j.infsof.2014.11.001}.

\end{thebibliography}

>>>>

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section*{#1}}
\newcommand{\ruleminor}[1]{\textbf{#1}}
%% END MACROS SECTION

% enumerate package lets us use letters instead of numbers
\usepackage{enumerate}
\usepackage{color}

\begin{document}
\vspace*{0.2in}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Making Research Software More Robust}
}
\newline
\\
{Morgan~Taschuk}\textsuperscript{1,\ddag *},
{Greg~Wilson}\textsuperscript{2,\ddag}
\\
\bigskip
\textbf{1} Genome Sequence Informatics, Ontario Institute for Cancer Research, Toronto, Ontario, Canada
\\
\textbf{2} Software Carpentry Foundation, https://software-carpentry.org/
\\
\bigskip
{\ddag} These authors contributed equally to this work.
\\
* morgan.taschuk@oicr.on.ca
\end{flushleft}

@@

\paragraph*{S1 Checklist.}
\label{S1_Checklist}
{\bf Robust software checklist.} A checklist summarizing these ten simple rules
to apply to your own software.

\bibliography{robust-software}
